A Note on Convergence Diagnostics for Multiple Imputation Algorithms

### 2019-12-12 Simulation/Writeup/NoteConvergence.Rnw
Comments Rosalie verwerkt, nog steeds te veel woorden...

To obtain valid inferences with MI, the variability between imputations should be properly represented \citep{rubin87, buur18}. If the variance between imputations is under-estimated, confidence intervals around estimates will be too narrow, which can yield spurious results. On the other hand, over-estimation of the variance between imputations results in unnecessarily wide confidence intervals, which can be costly because it lowers the statistical power. Since both of these situations are undesirable, imputations and their variability should be evaluated. Evaluation measures, however, are currently missing or under-developed in MI software, like the world-leading \pkg{mice} package \citep{mice} in \proglang{R} \citep{R}. %\textbf{ADD sentence to link eval measures to convergence!}
%Therefore, I will answer the following question: 'Which measures are vital for evaluating the validity of multiply imputed data?'.

The goal of this research project is to develop novel methodology and guidelines for evaluating MI methods. These evaluation measures and guidelines will subsequently be implemented in an interactive evaluation framework for multiple imputation to aid applied researchers in drawing valid inference from incomplete datasets. This note provides the theoretical foundation towards the diagnostic evaluation of the convergence of MI algorithms. % for diagnostics for evalua one of these evaluation measures that is vital in evaluating MI procedures: a diagnostic to assess convergence of the MI algorithm. 
For reasons of brevity, this note only focuses on the MI algorithm implemented in \pkg{mice} \cite{mice}. %The implementation limits itself to the MI algorithm 
%More specifically, this note focuses on the MI algorithm that is implemented in the \proglang{R} package \pkg{mice}: `Multiple Imputation using Chained Equations' (MICE) \textbf{[can be removed, can be found in the mice ref]}. 
To this end, we will evaluate how convergence of the imputation algorithm can be diagnosed.

@@

Let $Y$ denote an $n \times p$ matrix containing the data values on $p$ variables for all $n$ units in a sample. The collection of observed data values in $Y$ is denoted as $Y_{obs}$; the missing part of $Y$ is referred to as $Y_{mis}$. Response indicator $R$ shows whether a data value in $Y$ is missing or observed. The relation between $R$, $Y_{obs}$, and $Y_{mis}$ determines the missingness mechanism. This note only considers a `missing completely at random' (MCAR) mechanism, where the probability of being missing is equal for all $n \times p$ cells in $Y$.

In this note, the terms `unobserved' and `missing' data are used interchangeably. Both refer to $Y_{mis}$, e.g. `\texttt{NA}' values in \proglang{R} or `\texttt{999}' in \proglang{SPSS}. The terms `incomplete' or `observed' data denote $Y_{obs}$. Incomplete data is the starting point of the multiple imputation procedure. Figure \ref{fig:steps} provides a schematic overview of the steps involved with MI.

@@

This note focuses on the algorithmic properties of the imputation step. The algorithm employed within this step has an iterative nature. That is, before drawing $m$ imputed values for each missing data point in $Y_{mis}$, a `chain' of potential values is sampled. Each of the $m$ chains starts with an initial value, drawn randomly from $Y_{obs}$. The chains are terminated after a predefined number of iterations. Only the ultimate sample that a chain lands on is imputed and subsequently used in the analysis and pooling steps. The collection of samples across iterations (between the initial value and the imputed value) for each of the $m$ imputations will be referred to as an `imputation chain'. The number of iterations will be denoted with $t$.

@@

The multiple imputation algorithm in \pkg{mice} is a special case of Markov chain Monte Carlo (MCMC) methods--a framework of iterative algorithmic procedures. While methodology for diagnosing convergence of MI algorithms has not been systematically studied \citep{buur18}, several convergence diagnostics have been proposed for other types of MCMC methods and the framework in general.
% For the framework of itrIt is not known whether convergence diagnostics that are available for the general framework that MICE is a special case of are appropriate for the evaluation of MI data. This is the framework of Markoc chain Monte Carlo %Yet, reference manuals of promiment MI software do mention the importance of evaluating algorithmic convergence (e.g., \cite[p.XYZ]{mice}, \textbf{XYZ, XYZ}). 
This section provides a brief review of: 1) how convergence is defined in the general context of iterative algorithmic procedures; 2) what diagnostic tools are available; and 3) which of these may apply to MI algorithms.

@@

Most convergence diagnostics target either of the two components. The stationarity component of convergence may be evaluated with autocorrelation \citep[$AC$][]{scha97, gelm13}, numeric standard error \citep[or `MC error'][]{gewe92}, and Raftery and Lewis's (\citeyear{raft91}) procedure to determine how many iterations are necessary to diminish the effect of trending within chains. The mixing component can be assessed with the potential scale reduction factor $\widehat{R}$ \citep[widely referred to as `the Gelman-Rubin statistic']{gelm92}. With an adapted version of $\widehat{R}$, proposed by \cite{veht19}, we may also evaluate the stationarity component of convergence. This would make $\widehat{R}$ a general convergence diagnostic. The application of $\widehat{R}$ to assess stationarity has not been thoroughly investigated. Therefore, this study employs both $\widehat{R}$ and autocorrelation to investigate algorithmic convergence, as recommended by \cite[p.~898]{cowl96}.
%Therefore, the focus of this study is mainly on $\widehat{R}$. Stationarity will also be evaluated with autocorrelation as diagnostic, as recommended by \cite[p.~898]{cowl96}. 
Other convergence diagnostics are outside the scope of this study.\footnotemark 
\footnotetext{All of these methods evaluate the convergence of univariate scalar summaries (e.g., chain means or variances). These convergence diagnostics cannot diagnose convergence of multivariable statistics (i.e., relations between scalar summaries). \cite{buur18} proposed to implement multivariable evaluation by means of eigenvalue decomposition \cite{mack03}. This method is outside of the scope of the current study.}%  he eigenvector decomposition method proposed by McKay \citep{XYZ}.} These four methods, however, are outside of the scope of this study. Here, the focus is mainly on $\widehat{R}$ and autocorrelation.

@@

%The potential scale reduction factor $\widehat{R}$ is obtained as:
We can interpret $\widehat{R}$ as potential scale reduction factor, since it indicates by how much the variance of $\theta$ could be shrunken down if an infinite number of iterations per chain would be run \citep[$t \to \infty$;][]{gelm92}. High $\widehat{R}$-values would therefore indicate slow mixing of chains, e.g., because of dependence across chains on initial values. Once there is no dependence on initial values anymore, there is no added value of continuing iterations. The measure then diagnoses algorithmic convergence ($\widehat{R} = 1$). 
%If there is no added value compared to infinitely many iterations, the chains have converged. 
The conventionally acceptable threshold was $\widehat{R} < 1.2$ \cite{gelm92}. More recently, \cite{veht19} proposed a more stringent threshold: $\widehat{R} < 1.01$.

@@

It is not known whether $\widehat{R}$ and $AC$ are appropriate measures to diagnose convergence of MI algorithms. Assessing the stationarity component of convergence with $AC$ might be redundant, since high $AC$-values are implausible in MI procedures. That is, the randomness induced by the MI algorithm effectively mitigates the risk of dependency within chains. $AC$ would thus not be informative of the convergence of MI algorithms. $\widehat{R}$ may not be an appropriate diagnostic either, because it assumes over-dispersed initial values (i.e., the starting points of the chains are `far away' from the target distribution and each other). In \pkg{mice}, initial values of the algorithm are chosen randomly from the observed data. Therefore, we cannot be certain that the initial values are over-dispersed. %The initial parameter value is noodzakelijk. Daarom is het lastig om in MI that starten vanuit overdisp state. 
% Starting values of MICE chains: "For each j, fill in starting imputations $Y^0_j$ by random draws from $Y^{obs}_j$." \cite[\S~4.5.2]{buur18} before for loops over variables and imputations, see \url{https://stefvanbuuren.name/fimd/sec-FCS.html#def:mice}
Without over-dispersed initial states, $\widehat{R}$ may falsely diagnose convergence \citep{broo98}. %would not be sensitive enough to flag non-convergence of MI algorithms: "if over-dispersion does not hold, $\sigma_+^2$ can be too low, which can lead to falsely diagnosing convergence." \cite[p~437]{broo98}. 
This suggests that $\widehat{R}$ would not be sensitive enough to flag non-convergence of MI algorithms. An empirical finding, on the other hand, shows that $\widehat{R}$ can indicate non-convergence at unconventionally long chain lengths. While the default number of iterations in \pkg{mice} is five, $\widehat{R} > 1.1$ was observed after 50 iterations, and $\widehat{R} > 1.01$ up-to 150 iterations. This suggests that $\widehat{R}$ would over-estimate non-convergence of MI algorithms.

@@

This study evaluates whether $\widehat{R}$ and $AC$ can diagnose when the multiple imputation algorithm has converged. There is, however, no baseline measure available to evaluate their performance against. The current practice of assessing convergence is to visually inspect imputation chains for signs of non-mixing and non-stationarity \citep[\S~6.5.2]{buur18}. Visually assessing convergence, however, may be challenging to the untrained eye. \textbf{[This is problematic because. MAYBE REPLACE THIS PART!]} There is no scientific consensus on the convergence properties of multiple imputation algorithms \citep{taka17}, and in some situations, the default techniques in \pkg{mice} might not converge to stable target distributions at all \citep{murr18}. %Convergence diagnostics for MI methods have not been systematically studied \citep{buur18}.  Moreover, 
%A fundamental assumption of MICE is convergence of the algorithm. MICE is a type of Markov chain Monte Carlo (MCMC) algorithm. In general, the validity of inference resulting from MCMC algorithms is threatened by non-convergence. Hence we use convergence diagnostics to flag non-convergence. But it is not known whether conventional convergence diagnostics for MCMC methods work on MI data.
Therefore, convergence of the MI algorithms in \pkg{mice} should be monitored carefully. %the need for convergence diagnostics is extra pressing in the context of the MICE algorithm.

@@

This simulation study hypothesizes that $\widehat{R}$ will over-estimate non-convergence. %\textbf{[Or use:] Hypothesis based on \cite{lace07} is that the conventional acceptable level of $\widehat{R}$ is too strict for MI data. We expect that the simulation diagnostics will indicate valid inference before $\widehat{R}$ will.}

@@

To investigate the convergence properties of the \pkg{mice} algorithm, we perform model-based simulation of the MI procedure with varying imputation chain lengths. Each simulation condition has a different maximum number of iterations, from one to one-hundred iterations. We compute $\widehat{R}$ and autocorrelation (`convergence diagnostics') and performance measures (`simulation diagnostics') for each condition. The number of simulation runs per condition is 1000. %All simulation conditions are replicated 1000 times. %For each of the 100 conditions 1000 simulation runs are performed. for each of the 100 simulation conditions. \textbf{Estimands are convergence diagnostics. Performance measures are simulation diagnostics.  where for one through one hundred the Rhat and ... are calculated.} 
The simulation set-up consists of several steps, summarized in the pseudo-code below.\footnote{The complete \proglang{R} script of the simulation study is available on Github.}

@@

\subsection{Data simulation}
The simulated dataset is a finite population of $N=1000$. The data are simulated to solve a multiple linear regression complete data problem. The quantity of scientific interest is the estimated regression coefficient of predictor $X$ on outcome variable $Y$. The linear regression model is $Y \sim \beta_1 X + \beta_2 Z_1 + \beta_3 Z_2$, where $Y$ is the dependent variable, $X$ is an independent variable, and $Z_1$ and $Z_2$ are covariates. The data generating model of the predictors is a multivariate normal distribution with means structure $\mu$, and variance-covariance matrix $\Sigma$.

@@

Linear regression is performed using the \proglang{R} function \fct{lm}. The quantity of scientific interest $Q$ is the regression coefficient of $X$ on $Y$. $Q$ is estimated in each imputation, in each simulation condition, in each repetition. The $m = 5$ estimated regression coefficients $\hat{Q}$ are pooled according to Rubin's \citeyear{rubin87} rules with \pkg{mice} function \fct{pool}.

\subsection{Simulation diagnostics}
The simulation diagnostics are as recommended by \cite[\S~2.5.2]{buur18}. These evaluation criteria comprise of average bias, average confidence interval width, and empirical coverage rate across simulations. %"We expect that in accordance with Neyman (1934), at least 95 percent of the confidence intervals should contain the true population value, although some room for simulation error should be taken into account to counteract the finite nature of our simulations"\cite{schou18}.
We could also look at distributional characteristics, and plausibility of imputed values, see \cite{vinknd} (n.d.). For now, this is outside of the scope of this study. % Or use: Then evaluate the regular diagnostics of MI simulations, see Vink, n.d., and  convergence. Diagnostics include absolute bias of the estimated regression coefficient, confidence interval width, and empirical coverage rate across simulations. Convergence is evaluated with $\widehat{R}$, or potential scale reduction factor.

>>>>

To obtain valid inferences with MI, the variability between imputations should be properly represented \citep{rubin87, buur18}. If this variability is under-estimated, confidence intervals around estimates will be too narrow, which can yield spurious results. However, over-estimation of the variance between imputations results in unnecessarily wide confidence intervals, which can be costly because it lowers the statistical power. Since both of these situations are undesirable, imputations and their variability should be evaluated. Evaluation measures, however, are currently missing or under-developed in MI software, like the world-leading \pkg{mice} package \citep{mice} in \proglang{R} \citep{R}. %\textbf{ADD sentence to link eval measures to convergence!}
%Therefore, I will answer the following question: 'Which measures are vital for evaluating the validity of multiply imputed data?'.

The goal of this research project is to develop novel methodology and guidelines for evaluating MI methods. These tools will subsequently be implemented in an interactive evaluation framework for multiple imputation to aid applied researchers in drawing valid inference from incomplete datasets. This note provides the theoretical foundation towards the diagnostic evaluation of the convergence of MI algorithms. % for diagnostics for evalua one of these evaluation measures that is vital in evaluating MI procedures: a diagnostic to assess convergence of the MI algorithm. 
For reasons of brevity, this note only focuses on the MI algorithm implemented in \pkg{mice} \cite{mice}. %The implementation limits itself to the MI algorithm 
%More specifically, this note focuses on the MI algorithm that is implemented in the \proglang{R} package \pkg{mice}: `Multiple Imputation using Chained Equations' (MICE) \textbf{[can be removed, can be found in the mice ref]}. 
To this end, we will evaluate how convergence of the imputation algorithm can be diagnosed.

@@

Let $Y$ denote an $n \times p$ matrix containing the data values on $p$ variables for all $n$ units in a sample. The collection of observed data values in $Y$ is denoted as $Y_{obs}$; the missing part of $Y$ is referred to as $Y_{mis}$. \textbf{REMOVE? Response indicator $R$ shows whether a data value in $Y$ is missing or observed.} The relation between $R$, $Y_{obs}$, and $Y_{mis}$ determines the missingness mechanism. This note only considers a `missing completely at random' (MCAR) mechanism, where the probability of being missing is equal for all $n \times p$ cells in $Y$.

In this note, the terms `unobserved' and `missing' data are used interchangeably to refer to $Y_{mis}$. The terms `incomplete' or `observed' data denote $Y_{obs}$. Incomplete data is the starting point of the multiple imputation procedure. Figure \ref{fig:steps} provides an overview of the steps involved with MI.

@@

This note focuses on the algorithmic properties of the imputation step. The algorithm employed within this step has an iterative nature. That is, before drawing $m$ imputed values for each missing data point in $Y_{mis}$, a `chain' of potential values is sampled. Each of the $m$ chains starts with an initial value, drawn randomly from $Y_{obs}$. The chains are terminated after a predefined number of iterations. Only the ultimate sample that a chain lands on is imputed and subsequently used in the analysis and pooling steps. The collection of samples across iterations (between the initial value and the imputed value) for each of the $m$ imputations will be referred to as an `imputation chain'. The total number of iterations per chain will be denoted with $T$, where $t$ varies over the integers $1, 2, \dots, T$.

@@

There is no scientific consensus on the convergence properties of multiple imputation algorithms \citep{taka17}. Some default techniques in \pkg{mice} might not yield converged states at all \citep{murr18}. Algorithmic convergence should, therefore, be monitored carefully. In that respect is the current evaluation practice insuffient. That is, the  recommendation is to visually inspect imputation chains for signs of non-convergence, which may be challenging to the untrained eye \citep[\S~6.5.2]{buur18}. Quantitative evaluation of the convergence of MI algorithms would be preferred.

The multiple imputation algorithm in \pkg{mice} is a special case of Markov chain Monte Carlo (MCMC) methods---a framework of iterative algorithmic procedures. Within this framework, several convergence diagnostics have been proposed, but the application of these measures on MI algorithms has not been systematically studied \citep{buur18}.
% For the framework of itrIt is not known whether convergence diagnostics that are available for the general framework that MICE is a special case of are appropriate for the evaluation of MI data. This is the framework of Markoc chain Monte Carlo %Yet, reference manuals of promiment MI software do mention the importance of evaluating algorithmic convergence (e.g., \cite[p.XYZ]{mice}, \textbf{XYZ, XYZ}). 
This section provides a brief review of:% briefly reviews?
1) how convergence is defined in the general context of iterative algorithmic procedures; 2) what diagnostic tools are available; and 3) which of these may apply to MI algorithms.

@@

\textbf{[COULD BE SHORTER!]} Most convergence diagnostics target either of the two components. The stationarity component of convergence may be evaluated with autocorrelation \citep[$AC$; ][]{scha97, gelm13}, numeric standard error \citep[or `MC error'; ][]{gewe92}, and Raftery and Lewis's (\citeyear{raft91}) procedure to determine the effect of trending within chains. The mixing component can be assessed with the potential scale reduction factor $\widehat{R}$ \citep[a.k.a. `Gelman-Rubin statistic';][]{gelm92}. With an adapted version of $\widehat{R}$, proposed by \cite{veht19}, we might also evaluate the stationarity component of convergence. This would make $\widehat{R}$ a general convergence diagnostic. The application of $\widehat{R}$ to assess stationarity has not been thoroughly investigated. Therefore, this study employs both $\widehat{R}$ and autocorrelation to investigate convergence, as recommended by \cite[p.~898]{cowl96}.
%Therefore, the focus of this study is mainly on $\widehat{R}$. Stationarity will also be evaluated with autocorrelation as diagnostic, as recommended by \cite[p.~898]{cowl96}. 
Other convergence diagnostics are outside the scope of this study.\footnotemark 
\footnotetext{All of these methods evaluate the convergence of univariate scalar summaries (e.g., chain means or variances). These convergence diagnostics cannot diagnose convergence of multivariable statistics (i.e., relations between scalar summaries). \cite{buur18} proposed to implement multivariable evaluation by means of eigenvalue decomposition \cite{mack03}. This method is outside of the scope of the current study.}%  he eigenvector decomposition method proposed by McKay \citep{XYZ}.} These four methods, however, are outside of the scope of this study. Here, the focus is mainly on $\widehat{R}$ and autocorrelation.

@@

%The potential scale reduction factor $\widehat{R}$ is obtained as:
We can interpret $\widehat{R}$ as potential scale reduction factor, since it indicates by how much the variance of $\theta$ could be shrunken down if an infinite number of iterations per chain would be run \citep[$t \to \infty$;][]{gelm92}. High $\widehat{R}$-values would therefore indicate slow mixing of chains, e.g., because of dependence across chains on initial values. Once there is no dependence on initial values anymore, there is no added value of continuing iterations. \textbf{[MOGELIJK OVERBODIGE ZIN HIER]} The measure then diagnoses algorithmic convergence ($\widehat{R} = 1$). 
%If there is no added value compared to infinitely many iterations, the chains have converged. 
The conventionally acceptable threshold was $\widehat{R} < 1.2$ \cite{gelm92}. Recently, \cite{veht19} proposed a more stringent threshold: $\widehat{R} < 1.01$.

@@

%\textbf{HIER VALT TE SCHRAPPEN!} It is not known whether $\widehat{R}$ and $AC$ are appropriate measures to diagnose convergence of multiple imputation algorithms.

@@

This study evaluates whether $\widehat{R}$ and $AC$ could diagnose convergence of multiple imputation algorithms. There is, however, no baseline measure available to evaluate their performance against.\footnote{Only severely pathological cases of non-convergence stand out when visually inspecting the imputation chains.} We will assess the appropriateness of the two convergence diagnostics by comparison with simulation quantities (e.g., bias in estimating $Q$).

\textbf{We hypothesize that $\widehat{R}$ will over-estimate non-convergence. No hypothesis was formulated about AC, results are exploratory.
%
[MOVE THIS TO DISCUSSION?] Assessing the stationarity component of convergence with $AC$ might be redundant, since high $AC$-values are implausible in MI procedures. That is, the randomness induced by the MI algorithm effectively mitigates the risk of dependency within chains. $AC$ would thus not be informative of the convergence of MI algorithms. 
%
Moreover, we hypothesize that $\widehat{R}$ may not be an appropriate diagnostic either, because it assumes over-dispersed initial values (i.e., the starting points of the chains are `far away' from the target distribution and each other). In \pkg{mice}, initial values of the algorithm are chosen randomly from the observed data. Therefore, we cannot be certain that the initial values are over-dispersed. %The initial parameter value is noodzakelijk. Daarom is het lastig om in MI that starten vanuit overdisp state. 
% Starting values of MICE chains: "For each j, fill in starting imputations $Y^0_j$ by random draws from $Y^{obs}_j$." \cite[\S~4.5.2]{buur18} before for loops over variables and imputations, see \url{https://stefvanbuuren.name/fimd/sec-FCS.html#def:mice}
Without over-dispersed initial states, $\widehat{R}$ may falsely diagnose convergence \citep{broo98}. %would not be sensitive enough to flag non-convergence of MI algorithms: "if over-dispersion does not hold, $\sigma_+^2$ can be too low, which can lead to falsely diagnosing convergence." \cite[p~437]{broo98}. 
This suggests that $\widehat{R}$ would not be sensitive enough to flag non-convergence of MI algorithms. However, an empirical finding by \cite{lace07} shows that $\widehat{R}$ can indicate non-convergence at unconventionally long chain lengths. While the default number of iterations in \pkg{mice} is five, $\widehat{R} > 1.1$ was observed after 50 iterations, and $\widehat{R} > 1.01$ up-to 150 iterations. This suggests that $\widehat{R}$ would over-estimate non-convergence of MI algorithms. }

%Convergence diagnostics for MI methods have not been systematically studied \citep{buur18}.  Moreover, 
%A fundamental assumption of MICE is convergence of the algorithm. MICE is a type of Markov chain Monte Carlo (MCMC) algorithm. In general, the validity of inference resulting from MCMC algorithms is threatened by non-convergence. Hence we use convergence diagnostics to flag non-convergence. But it is not known whether conventional convergence diagnostics for MCMC methods work on MI data.
%the need for convergence diagnostics is extra pressing in the context of the MICE algorithm.

@@

%This simulation study hypothesizes that $\widehat{R}$ will over-estimate non-convergence. %\textbf{[Or use:] Hypothesis based on \cite{lace07} is that the conventional acceptable level of $\widehat{R}$ is too strict for MI data. We expect that the simulation diagnostics will indicate valid inference before $\widehat{R}$ will.}

@@

%To investigate the convergence properties of the multiple imputation algorithm in \pkg{mice}, w
We use model-based simulation to perform multiple imputation under 100 simulation conditions. In each condition, the MI algorithm comprises a different imputation chain length ($T = 1, 2, \dots, 100$). The number of simulation runs per condition is 1000. Convergence diagnostics ($\widehat{R}$ and autocorrelation) and simulation diagnostics (bias, confidence interval width and coverage) are computed for each simulation condition, and aggregated across simulation runs.
%We compute $\widehat{R}$ and autocorrelation (`convergence diagnostics') and performance measures (`simulation diagnostics') for each condition. %All simulation conditions are replicated 1000 times. %For each of the 100 conditions 1000 simulation runs are performed. for each of the 100 simulation conditions. \textbf{Estimands are convergence diagnostics. Performance measures are simulation diagnostics.  where for one through one hundred the Rhat and ... are calculated.} 
The simulation set-up consists of several steps, summarized in the pseudo-code below.\footnote{The complete \proglang{R} script of the simulation study is available on Github.}

@@

\subsection{Data simulation}
The simulated dataset is a finite population of $N=1000$. The data are simulated to solve a multiple linear regression problem, where dependent variable $Y$ is regressed on independent variable $X$, and covariates $Z_1 \text{ and } Z_2$: $Y \sim \beta_1 X + \beta_2 Z_1 + \beta_3 Z_2$. The quantity of scientific interest is regression coefficient $\beta_1$. The data generating model is a multivariate normal distribution with means structure $\mu$, and variance-covariance matrix $\Sigma$.

@@

Linear regression is performed using the \proglang{R} function \fct{lm}. The quantity of scientific interest $Q$ is the regression coefficient of $X$ on $Y$. $Q$ is estimated in each imputation, in each simulation condition, in each repetition. The $m = 5$ estimated regression coefficients $\hat{Q}$ are pooled according to Rubin's \citeyear{rubin87} rules with \pkg{mice} function \fct{pool}. Variance is computed accroding to finite population pooling \textbf{Vink and Van Buuren, 2014??}.

\subsection{Simulation diagnostics}
The simulation diagnostics are as recommended by \citep[\S~2.5.2]{buur18}. These evaluation criteria comprise of average bias, average confidence interval width, and empirical coverage rate across simulations.% %"We expect that in accordance with Neyman (1934), at least 95 percent of the confidence intervals should contain the true population value, although some room for simulation error should be taken into account to counteract the finite nature of our simulations"\cite{schou18}.
\footnote{We could also look at distributional characteristics, and plausibility of imputed values, see \cite{vinknd} (n.d.). For now, this is outside of the scope of this study.} % Or use: Then evaluate the regular diagnostics of MI simulations, see Vink, n.d., and  convergence. Diagnostics include absolute bias of the estimated regression coefficient, confidence interval width, and empirical coverage rate across simulations. Convergence is evaluated with $\widehat{R}$, or potential scale reduction factor.
